### 2021-09-21 documentos/pce.tex
etc

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\left\{ \frac{1}{2^{N/2}}\sigma_{\vec
\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $1/2^{N/2} \left\{\sigma_{\vec \alpha} \right\}_{\vec \alpha}$
 \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

>>>>

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$. Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
 \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia} \ddnote{De momento no he encontrado alguna reference, para qubits si, pero para los generales no, estoy checando de nuevo el paper de Ruskai para entender que tanto se solapan, a ver si puedo decir algo}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.
